Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-06 paper/main.tex
revise descriptions of contrasts v1

\todo[inline]{SE: das mit den "five additional categories" habe ich nicht
verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
durchdrungen, und ich glaube damit werde ich nicht alleine sein. COH: }
% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AO stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.

@@

% AV events
For the analysis of the AV stimulus, we used a previously published annotation
[of the 869] movie cuts and depicted locations \citep{haeusler2016cutanno} to
created regressors based on the kind of location that is depicted in the movie
frame after each cut.

@@

% todo
\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
ein setting "familiar"?; COH: should be clearer now; maybe rephrase into a
couple of sentences to improve readability}
% AV regressors/events
Each location was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

% to do
\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
zwischen zwei Gesichtern sein?!?; COH: that should be clearer now as the
explanation of the regressors immediately follows the description of the
annotation}
% irrespectible of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).

%%%%%% do not speak of isolate %%%%%%
% AV COPEs: intro
The rationale that this procedure would still be able to isolate the PPA was
twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal, grill2006repetition}.

% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a
movie cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.
% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).

@@

\todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv
durchblickt. Was wurde da gegen was kontrastiert?}
% we have fixed stimuli
Compared to previous studies we did not design the stimulus material and
experimentally controlled conditions for the purpose of optimal localization
performance since we used fixed stimuli.
% 8 + 5 contrasts
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to operationalize ``spatial perception'' compared to
``non-spatial'' perception.\todo{big ouff\dots}
% test for robustness
Creating more than just one contrast for the two fixed stimuli also let us test
for/the robustness of our results across varying ways operationalization.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

% AO COPEs: intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for three reasons and thus are not included in
the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``in Greenbow'', ``in a
disco'', ''black and white film recordings'') whereas a picture of the verbally
described scene would be perceptually richer,
% hierarchical categories
(b) they also comprise words that could count as a member of another category in
case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as a teenager'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.
% furniture
We did not use the category ``furniture'' (\texttt{furn}) as a regressor of
interest in any contrasts because nouns in this category were usually big and
heavy. In a serial stream of auditory information, participants could perceive
furniture-related nouns as either a geometry-defining local scene element or as
an isolated object. Hence we did not use this category as regressor of interest
to reduce noise.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with moments
of cuts and therefore possibly correlated with a accompanying change in the
soundscape.

\todo[inline]{MH: I think it's better to explain the rationale of the regressors
    here in the context of the contrasts and not already above in the list of
    created regressors: COH: yes, I checked that. Above is just a short
    list/explanation except for ``no cut'' condition. imo it makes more sense to
explain it there but maybe I cannot get the reason why you think it fits here
better}

% following contrasts
We created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}) by using regressors based on regressors of the AO
stimulus.

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only stimulus (AO).
Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} = body, bodypart,
    fahead, object, sex\_f, sex\_m).
Contrasts 9-13 serve as negative control at the moments of movie cuts that could
    correlate with changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & groom, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

>>>>

\todo[inline]{SE: das mit den "five additional categories" habe ich nicht
verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
durchdrungen, und ich glaube damit werde ich nicht alleine sein. COH: }
% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AO stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.
% convolving
Events for all regressors of the AV stimulus were convolved with a
double gamma hemodynamic response function (HRF).

@@

% AV events
For the analysis of the AV stimulus, we used a previously published annotation
[of the 869] movie cuts and depicted locations \citep{haeusler2016cutanno} to
created regressors based on the kind of location that is depicted in the movie
frame after a cut.

@@

\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
ein setting "familiar"?; COH: should be clearer now; maybe rephrase into a
couple of sentences to improve readability}

% AV regressors/events
Each location was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

% irrespectible of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).
% AV COPEs: intro
The rationale that this approach would still yield categories correlating with
increased hemodynamic activity in the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal, grill2006repetition}.
% null regressor
As for the regressors for AO stimulus, a null regressor was chosen for a
regressor in a segment if that segment did not contain an event of the
corresponding category.
% no cut condition: intro
A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
created as a control condition and to create negative control contrasts:
% procedure
Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
a minimum distance of \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

\todo[inline]{mention low-level feature events for AV here as well}

% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie can be found in Table \ref{tab:av-events}.
% convolving
Events for all regressors of the AV stimulus were convolved with a
double gamma hemodynamic response function (HRF).

@@

\todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv
durchblickt. Was wurde da gegen was kontrastiert?}

% why several contrasts
To test the robustness of our approach,  we created several contrasts for every
stimulus.
%
We operationalized the perception of spatial information compared to the
perception of ``non-spatial'' information differently in eight $t$-contrasts for
the AO stimulus (see Table \ref{tab:ao-contrasts}) and five $t$-contrasts for
the AV stimulus (see Table \ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in \todo{differ in what?
``localization performance'' isn't well phrased. How ``well'', ``nice'' the
results are?} since used event categories differed a) in how well the averaged
events reflected spatial information, and b) in event counts
% thus: primary contrasts
We chose one ``primary contrast'' for every stimulus before running the
analyses.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the primary contrast of the AO stimulus we contrasted \texttt{geo} and
\texttt{groom} with all non-geometry related categories
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the primary contrast of the AV stimulus we contrasted

% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.\todo{oh, lord!}

% for example, AO stimulus AO COPEs: intro
For example, the categories \texttt{se\_new} and \texttt{se\_old} of the AO
stimulus were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast.
%
In a serial stream of auditory information, these nouns could be perceived
differently by different subjects as either a geometry-defining scene elements
or as an isolated object.

% why not locale change

\paragraph{control contrasts: AO \& AV}

% intro

% AO
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with moments
of cuts and therefore possibly correlated with a accompanying change in the
soundscape.

% AV
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}) by using regressors based on regressors of the AO
stimulus.

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus (AO).
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old & non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}
